Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is a merged and final version of two conference papers, \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}, with a unified and streamlined presentation.}

### 2020-07-18 journal paper/content/sec-intro.tex
Added a footnote re time-discounting.

\asedit{Principals' utilities (and, accordingly, bandit rewards) are not discounted with time. While much of the early work focuses on  time-discounted bandits \citep{Gittins-book11}, non-discounted  formulations are prevalent in the bandits literature over the past two decades \citep{slivkins-MABbook,LS19bandit-book}, and better correspond to practical deployments \citep[\eg][]{DS-arxiv}. Moreover, the distinctions between better and worse bandit algorithms are not as well-understood under time-discounting.}

>>>>

\asedit{Principals' utilities (and, accordingly, bandit rewards) are not discounted with time.%
\footnote{However, our main theoretical result on the greedy algorithm extends to time-discounted rewards, see Section~\ref{sec:theory-extensions}.}
 While much of the early work focuses on  time-discounted bandits \citep{Gittins-book11}, non-discounted  formulations are prevalent in the bandits literature over the past two decades \citep{slivkins-MABbook,LS19bandit-book}, and better correspond to practical deployments \citep[\eg][]{DS-arxiv}. Moreover, the distinctions between better and worse bandit algorithms are not as well-understood under time-discounting.}
